Persistent somatic symptoms are key to individual illness perception at one year after COVID-19 in a cross-sectional analysis of a prospective cohort study

### 2023-03-20 paper/markdown/manuscript.Rmd
Compacting footnotes of Suppl. Tables

<span custom-style = 'revision'>Generally, differences between the IP clusters in PSS readouts like 
PSS number (Kruskal-Wallis test: `r clust_chara$test_results$fup %>% filter(variable == 'sympt_number') %>% .$plot_cap`), 
fatigue rating (`r clust_chara$test_results$fup %>% filter(variable == 'Chalder_FS') %>% .$plot_cap`), 
significant fatigue ($\chi^2$ test: `r clust_chara$test_results$fup %>% filter(variable == 'Chalder_FS-bimodal') %>% .$plot_cap`), 
sleep problems (`r clust_chara$test_results$fup %>% filter(variable == 'sleep_sympt') %>% .$plot_cap`) or 
hair loss (`r clust_chara$test_results$fup %>% filter(variable == 'hair_loss_sympt') %>% .$plot_cap`) and differences in rehabilitation rates (`r clust_chara$test_results$fup %>% filter(variable == 'rehabilitation') %>% .$plot_cap`) were of moderate-to-large effect size.
Effects of differences in 
lung computed tomography abnormality (`r clust_chara$test_results$fup %>% filter(variable == 'ct_severity_any') %>% .$plot_cap`), 
chest computed tomography abnormality scoring (`r clust_chara$test_results$fup %>% filter(variable == 'ct_severity_score') %>% .$plot_cap`), 
lung function testing deficits (`r clust_chara$test_results$fup %>% filter(variable == 'lufo_red') %>% .$plot_cap`) or 
diastolic dysfunction (`r clust_chara$test_results$fup %>% filter(variable == 'diastolic_dysf') %>% .$plot_cap`) were substantially weaker (__Supplementary Table S8__).</span>

>>>>

<span custom-style = 'revision'>Generally, differences between the IP clusters in PSS readouts like 
PSS number (Kruskal-Wallis test: `r clust_chara$test_results$fup %>% filter(variable == 'sympt_number') %>% .$plot_cap`), 
fatigue rating (`r clust_chara$test_results$fup %>% filter(variable == 'Chalder_FS') %>% .$plot_cap`), 
significant fatigue ($\chi^2$ test: `r clust_chara$test_results$fup %>% filter(variable == 'Chalder_FS_bimodal') %>% .$plot_cap`), 
sleep problems (`r clust_chara$test_results$fup %>% filter(variable == 'sleep_sympt') %>% .$plot_cap`) or 
hair loss (`r clust_chara$test_results$fup %>% filter(variable == 'hair_loss_sympt') %>% .$plot_cap`) and differences in rehabilitation rates (`r clust_chara$test_results$fup %>% filter(variable == 'rehabilitation') %>% .$plot_cap`) were of moderate-to-large effect size.
Effects of differences in 
lung computed tomography abnormality (`r clust_chara$test_results$fup %>% filter(variable == 'ct_severity_any') %>% .$plot_cap`), 
chest computed tomography abnormality scoring (`r clust_chara$test_results$fup %>% filter(variable == 'ct_severity_score') %>% .$plot_cap`), 
lung function testing deficits (`r clust_chara$test_results$fup %>% filter(variable == 'lufo_red') %>% .$plot_cap`) or 
diastolic dysfunction (`r clust_chara$test_results$fup %>% filter(variable == 'diastolic_dysf') %>% .$plot_cap`) were substantially weaker (__Supplementary Table S8__).</span>

### 2023-03-20 paper/markdown/supplementary_material.Rmd
Compacting footnotes of Suppl. Tables

flextable::flextable(suppl_tbl$modeling_vars) %>% 
  width(1, width = 14, unit = 'cm') %>% 
  theme_vanilla

@@

flextable::flextable(suppl_tbl$excluded) %>% 
  width(1, width = 4.8, unit = 'cm') %>% 
  width(2:3, width = 3.5, unit = 'cm') %>% 
  width(4, width = 2.5, unit = 'cm') %>% 
  width(5, width = 2.1, unit = 'cm') %>% 
  footnote(1, 4:5, 
           value = as_paragraph('Categorical variables: \u03C7\u00B2 test with Cramer V effect size statistic, numeric variables: Mann-Whitney test with r effect size statistic'), 
           ref_symbols = 'a', 
           part = 'header') %>% 
  footnote(2, 1, 
           value = as_paragraph('WHO ordinal scale for clinical improvement'), 
           ref_symbols = 'b', 
           part = 'body') %>% 
  footnote(5, 1, 
           value = as_paragraph('Six minute walking distance'), 
           ref_symbols = 'b', 
           part = 'body') %>% 
  footnote(6, 1, 
           value = as_paragraph('Blood hemoglobin'), 
           ref_symbols = 'b', 
           part = 'body') %>% 
  footnote(7, 1, 
           value = as_paragraph('Serum ferritin'), 
           ref_symbols = 'b', 
           part = 'body') %>% 
  theme_vanilla()

@@

flextable::flextable(suppl_tbl$fup) %>% 
  width(1, width = 3.6, unit = 'cm') %>% 
  width(2:5, width = 3.2, unit = 'cm') %>% 
  width(6, width = 2.4, unit = 'cm') %>% 
  width(7, width = 2.1, unit = 'cm') %>%
  footnote(1, 6:7, 
           value = as_paragraph('Categorical variables: \u03C7\u00B2 test with Cramer V effect size statistic, numeric variables: Kruskal-Wallis test with \u03B7\u00B2 effect size statistic'), 
           ref_symbols = 'a', 
           part = 'header') %>% 
  footnote(2:3, 1, 
           value = as_paragraph('PSS: persistent somatic symptoms'), 
           ref_symbols = 'c', 
           part = 'body') %>% 
  footnote(4, 1, 
           value = as_paragraph('ECOG: Eastern Cooperative Oncology Group performance score'), 
           ref_symbols = 'c', 
           part = 'body') %>% 
  footnote(5, 1, 
           value = as_paragraph('mMRC: Modified Medical Research Council dyspnea score'), 
           ref_symbols = 'd', 
           part = 'body') %>% 
  footnote(13:14, 1, 
           value = as_paragraph("CFS: Chalder's Fatigure Score"), 
           ref_symbols = 'e', 
           part = 'body') %>% 
  footnote(15, 1, 
           value = as_paragraph('Lung function testing abnormality: FVC < 80% or FEV1 < 80% or TLC < 80% or DLCO < 80% predicted or FEV1:FVC < 70% predicted reference value'), 
           ref_symbols = 'f', 
           part = 'body') %>% 
  footnote(17, 1, 
           value = as_paragraph('Chest computer tomography severity score'), 
           ref_symbols = 'g', 
           part = 'body') %>% 
  footnote(19, 1, 
           value = as_paragraph('SMWD: Six minute walking distance'), 
           ref_symbols = 'h', 
           part = 'body') %>% 
  footnote(20, 1, 
           value = as_paragraph('SMWD, difference between the actual and reference value'), 
           ref_symbols = 'i', 
           part = 'body') %>% 
  theme_vanilla

@@

flextable::flextable(suppl_tbl$biochemistry_fup) %>% 
  width(1, width = 2.5, unit = 'cm') %>% 
  width(2:5, width = 3.5, unit = 'cm') %>% 
  width(6, width = 2.4, unit = 'cm') %>% 
  width(7, width = 2.1, unit = 'cm') %>%
  footnote(1, 6:7, 
           value = as_paragraph('Categorical variables: \u03C7\u00B2 test with Cramer V effect size statistic, numeric variables: Kruskal-Wallis test with \u03B7\u00B2 effect size statistic'), 
           ref_symbols = 'a', 
           part = 'header') %>% 
  footnote(2, 1, 
           value = as_paragraph('Females: hemoglobin (Hb) < 120 g/dL, males: Hb < 140 g/dL'), 
           ref_symbols = 'b', 
           part = 'body') %>% 
  footnote(3, 1, 
           as_paragraph('Blood hemoglobin'), 
           ref_symbols = 'c', 
           part = 'body') %>% 
  footnote(4, 1, 
           as_paragraph('Serum ferritin'), 
           ref_symbols = 'd', 
           part = 'body') %>%
  footnote(5, 1, 
           as_paragraph('Serum transferrin saturation'), 
           ref_symbols = 'e', 
           part = 'body') %>% 
  footnote(6, 1, 
           as_paragraph('Serum soluble transferrin receptor'), 
           ref_symbols = 'f', 
           part = 'body') %>% 
  footnote(8, 1, 
           as_paragraph('Serum N-terminal pro-brain natriuretic peptide'), 
           ref_symbols = 'g', part = 'body') %>% 
  footnote(10, 1, as_paragraph('Serum C-reactive protein'), 
           ref_symbols = 'h', 
           part = 'body') %>% 
  footnote(11, 1, 
           as_paragraph('Blood glycated hamoglobin'), 
           ref_symbols = 'i', 
           part = 'body') %>% 
  theme_vanilla

@@

flextable::flextable(suppl_tbl$gender) %>% 
  width(1, width = 5.2, unit = 'cm') %>% 
  width(2:3, width = 3.5, unit = 'cm') %>% 
  width(4, width = 2.5, unit = 'cm') %>% 
  width(5, width = 2.1, unit = 'cm') %>% 
  footnote(1, 4:5, 
           value = as_paragraph('Categorical variables: \u03C7\u00B2 test with Cramer V effect size statistic, numeric variables: Mann-Whitney test with r effect size statistic'), 
           ref_symbols = 'a', 
           part = 'header') %>% 
  footnote(2, 1, 
           value = as_paragraph('Former or active smoker'), 
           ref_symbols = 'b', 
           part = 'body') %>% 
  footnote(3, 1, 
           value = as_paragraph('Overweight: body mass index 25 - 30 kg/m\u00B2, obesity: > 30 kg/m\u00B2'), 
           ref_symbols = 'c', 
           part = 'body') %>% 
  footnote(5, 1, 
           value = as_paragraph('WHO ordinal scale for clinical improvement'), 
           ref_symbols = 'd', 
           part = 'body') %>% 
  footnote(7:8, 1, 
           value = as_paragraph('PSS: persistent somatic symptoms'), 
           ref_symbols = 'e', 
           part = 'body') %>% 
  footnote(9, 1, 
           value = as_paragraph('mMRC: Modified Medical Research Council dyspnea score'), 
           ref_symbols = 'f', 
           part = 'body') %>% 
  footnote(11, 1, 
           value = as_paragraph('Chest computer tomography severity score'), 
           ref_symbols = 'g', 
           part = 'body') %>% 
  footnote(12, 1, 
           value = as_paragraph('Blood hemoglobin'), 
           ref_symbols = 'h', 
           part = 'body') %>% 
  footnote(13, 1, 
           value = as_paragraph('Serum ferritin'), 
           ref_symbols = 'i', 
           part = 'body') %>% 
  theme_vanilla

@@

flextable::flextable(suppl_tbl$respi) %>% 
  width(1, width = 4.8, unit = 'cm') %>% 
  width(2:3, width = 3.3, unit = 'cm') %>% 
  width(4, width = 2.5, unit = 'cm') %>% 
  width(5, width = 2.1, unit = 'cm') %>% 
  footnote(1, 4:5, 
           value = as_paragraph('Categorical variables: \u03C7\u00B2 test with Cramer V effect size statistic, numeric variables: Mann-Whitney test with r effect size statistic'), 
           ref_symbols = 'a', 
           part = 'header') %>% 
  footnote(5:6, 1, 
           value = as_paragraph("CFS: Chalder's fatigue score"), 
           ref_symbols = 'b', 
           part = 'body') %>% 
  footnote(7, 1, 
           as_paragraph('Lung function testing abnormality: FVC < 80% or FEV1 < 80% or TLC < 80% or DLCO < 80% predicted or FEV1:FVC < 70% predicted reference value'), 
           ref_symbols = 'c', 
           part = 'body') %>% 
  footnote(8:12, 1, 
           as_paragraph('BIPQ: brief illness perception questionnaire'), 
           ref_symbols = 'd', 
           part = 'body') %>% 
  theme_vanilla

@@

flextable::flextable(suppl_tbl$ipq_clusters) %>% 
  width(1, width = 5.4, unit = 'cm') %>% 
  width(2:4, width = 3, unit = 'cm') %>% 
  width(5, width = 2.5, unit = 'cm') %>% 
  width(6, width = 2.1, unit = 'cm') %>%
  footnote(1, 5:6, 
           value = as_paragraph('Categorical variables: \u03C7\u00B2 test with Cramer V effect size statistic, numeric variables: Kruskal-Wallis test with \u03B7\u00B2 effect size statistic'), 
           ref_symbols = 'a', 
           part = 'header') %>% 
  footnote(2, 1, 
           value = as_paragraph('Former or active smoker'), 
           ref_symbols = 'b', 
           part = 'body') %>% 
  footnote(5, 1, 
           value = as_paragraph('WHO ordinal scale for clinical improvement'), 
           ref_symbols = 'c', 
           part = 'body') %>% 
  footnote(6:7, 1, 
           value = as_paragraph('PSS: persistent somatic symptoms'), 
           ref_symbols = 'd', 
           part = 'body') %>% 
  footnote(8, 1, 
           value = as_paragraph('ECOG: Eastern Cooperative Oncology Group performance score'), 
           ref_symbols = 'e', 
           part = 'body') %>% 
  footnote(9, 1, 
           value = as_paragraph('mMRC: Modified Medical Research Council dyspnea score'), 
           ref_symbols = 'f', 
           part = 'body') %>% 
  footnote(13:14, 1, value = as_paragraph("Chalder's Fatigure Score"), 
           ref_symbols = 'g', 
           part = 'body') %>% 
  footnote(15, 1, 
           value = as_paragraph('Lung function testing abnormality: FVC < 80% or FEV1 < 80% or TLC < 80% or DLCO < 80% predicted or FEV1:FVC < 70% predicted reference value'), 
           ref_symbols = 'h', 
           part = 'body') %>% 
  theme_vanilla

>>>>

flextable::flextable(suppl_tbl$modeling_vars) %>% 
  width(1, width = 14, unit = 'cm') %>% 
  footnote(1, 1, 
           value = as_paragraph("CVD: cardiovascular disease; #: number of; CKD: chronic kidney disease; GID: gastrointestinal disease; PSS: persistent somatic symptoms; CFS: Chalder's fatigue score; SMWD: six-minute walking distance; SMWD vs ref.: Difference of SMWD and the expected reference SMWD value; LFT: lung function testing; CT: computed tomography of the chest; HB: blood hemoglobin; FT: serum ferritin; TF-Sat: transferrin saturation; sTFR: serum soluble transferrin receptor; NT-proBNP: serum N-terminal pro-brain natriuretic peptide; CRP: serum C-reactive protein; HbA1c: glycated blood Hb"), 
           part = 'header', 
           ref_symbols = 'a') %>% 
  theme_vanilla

@@

flextable::flextable(suppl_tbl$excluded) %>% 
  width(1, width = 4.8, unit = 'cm') %>% 
  width(2:3, width = 3.5, unit = 'cm') %>% 
  width(4, width = 2.5, unit = 'cm') %>% 
  width(5, width = 2.1, unit = 'cm') %>% 
  footnote(1, 1, 
           value = as_paragraph('WHO COVID-19 severity: WHO ordinal scale for clinical improvement; SMWD: Six minute walking distance; Hb: Blood hemoglobin; FT: serum ferritin'), 
           ref_symbols = 'a', 
           part = 'header') %>% 
  footnote(1, 4:5, 
           value = as_paragraph('Categorical variables: \u03C7\u00B2 test with Cramer V effect size statistic, numeric variables: Mann-Whitney test with r effect size statistic'), 
           ref_symbols = 'b', 
           part = 'header') %>% 
  theme_vanilla()

@@

flextable::flextable(suppl_tbl$fup) %>% 
  width(1, width = 3.6, unit = 'cm') %>% 
  width(2:5, width = 3.2, unit = 'cm') %>% 
  width(6, width = 2.4, unit = 'cm') %>% 
  width(7, width = 2.1, unit = 'cm') %>%
  footnote(1, 1, 
           value = as_paragraph("PSS: persistent somatic symptoms; ECOG: Eastern Cooperative Oncology Group performance score; mMRC: Modified Medical Research Council dyspnea score; CFS: Chalder's fatigure score; LFT: lung function testing; CT: computed tomography of the chest; SMWD: Six minute walking distance; SMWD vs reference: SMWD, difference between the actual and reference value"), 
           part = 'header', 
           ref_symbols = 'a') %>% 
  footnote(1, 6:7, 
           value = as_paragraph('Categorical variables: \u03C7\u00B2 test with Cramer V effect size statistic, numeric variables: Kruskal-Wallis test with \u03B7\u00B2 effect size statistic'), 
           ref_symbols = 'b', 
           part = 'header') %>% 
  footnote(15, 1, 
           value = as_paragraph('Lung function testing abnormality: FVC < 80% or FEV1 < 80% or TLC < 80% or DLCO < 80% predicted or FEV1:FVC < 70% predicted reference value'), 
           ref_symbols = 'c', 
           part = 'body') %>% 
  theme_vanilla

@@

flextable::flextable(suppl_tbl$biochemistry_fup) %>% 
  width(1, width = 2.5, unit = 'cm') %>% 
  width(2:5, width = 3.5, unit = 'cm') %>% 
  width(6, width = 2.4, unit = 'cm') %>% 
  width(7, width = 2.1, unit = 'cm') %>%
  footnote(1, 1, 
           value = as_paragraph('Hb: blood hemoglobin; FT: serum ferritin; TF-Sat: serum transferrin saturation; sTFR: serum soluble transferrin receptor; NT-pro-BNP: serum N-terminal pro-brain natriuretic peptide; CRP: serum C-reactive protein; HbA1c: glycated blood Hb'), 
           part = 'header', 
           ref_symbols = 'a') %>% 
  footnote(1, 6:7, 
           value = as_paragraph('Categorical variables: \u03C7\u00B2 test with Cramer V effect size statistic, numeric variables: Kruskal-Wallis test with \u03B7\u00B2 effect size statistic'), 
           ref_symbols = 'b', 
           part = 'header') %>% 
  footnote(2, 1, 
           value = as_paragraph('Females: hemoglobin (Hb) < 120 g/dL, males: Hb < 140 g/dL'), 
           ref_symbols = 'c', 
           part = 'body') %>% 
  theme_vanilla

@@

flextable::flextable(suppl_tbl$gender) %>% 
  width(1, width = 6, unit = 'cm') %>% 
  width(2:3, width = 3.5, unit = 'cm') %>% 
  width(4, width = 2.5, unit = 'cm') %>% 
  width(5, width = 2.1, unit = 'cm') %>% 
  footnote(1, 1, 
           value = as_paragraph('WHO COVID-19 severity: WHO ordinal scale for clinical improvement; PSS: persistent somatic symptoms; mMRC: Modified Medical Research Council dyspnea score; CT: computed tomography of the chest; Hb: blood hemoglobin; FT: serum ferritin; BIPQ: brief illness perception questionnaire'), 
           part = 'header', 
           ref_symbols = 'a') %>% 
  footnote(1, 4:5, 
           value = as_paragraph('Categorical variables: \u03C7\u00B2 test with Cramer V effect size statistic, numeric variables: Mann-Whitney test with r effect size statistic'), 
           ref_symbols = 'b', 
           part = 'header') %>% 
  footnote(2, 1, 
           value = as_paragraph('Former or active smoker'), 
           ref_symbols = 'c', 
           part = 'body') %>% 
  footnote(3, 1, 
           value = as_paragraph('Overweight: body mass index 25 - 30 kg/m\u00B2, obesity: > 30 kg/m\u00B2'), 
           ref_symbols = 'd', 
           part = 'body') %>% 
  theme_vanilla

@@

flextable::flextable(suppl_tbl$respi) %>% 
  width(1, width = 6, unit = 'cm') %>% 
  width(2:3, width = 3.3, unit = 'cm') %>% 
  width(4, width = 2.5, unit = 'cm') %>% 
  width(5, width = 2.1, unit = 'cm') %>% 
  footnote(1, 1, 
           value = as_paragraph("CFS: Chalder's fatigue score; BIPQ: brief illness perception questionnaire"), 
           ref_symbols = 'a', 
           part = 'header') %>% 
  footnote(1, 4:5, 
           value = as_paragraph('Categorical variables: \u03C7\u00B2 test with Cramer V effect size statistic, numeric variables: Mann-Whitney test with r effect size statistic'), 
           ref_symbols = 'b', 
           part = 'header') %>% 
  footnote(7, 1, 
           as_paragraph('Lung function testing abnormality: FVC < 80% or FEV1 < 80% or TLC < 80% or DLCO < 80% predicted or FEV1:FVC < 70% predicted reference value'), 
           ref_symbols = 'c', 
           part = 'body') %>% 
  theme_vanilla

@@

flextable::flextable(suppl_tbl$ipq_clusters) %>% 
  width(1, width = 5.4, unit = 'cm') %>% 
  width(2:4, width = 3, unit = 'cm') %>% 
  width(5, width = 2.5, unit = 'cm') %>% 
  width(6, width = 2.1, unit = 'cm') %>%
  footnote(1, 1, 
           value = as_paragraph("WHO COVID-19 severity: WHO ordinal scale for clinical improvement; PSS: persistent somatic symptoms; ECOG: Eastern Cooperative Oncology Group performance score; mMRC: Modified Medical Research Council dyspnea score; CFS: Chalder's Fatigure Score"), 
           part = 'header', 
           ref_symbols = 'a') %>% 
  footnote(1, 5:6, 
           value = as_paragraph('Categorical variables: \u03C7\u00B2 test with Cramer V effect size statistic, numeric variables: Kruskal-Wallis test with \u03B7\u00B2 effect size statistic'), 
           ref_symbols = 'b', 
           part = 'header') %>% 
  footnote(2, 1, 
           value = as_paragraph('Former or active smoker'), 
           ref_symbols = 'c', 
           part = 'body') %>% 
  footnote(15, 1, 
           value = as_paragraph('Lung function testing abnormality: FVC < 80% or FEV1 < 80% or TLC < 80% or DLCO < 80% predicted or FEV1:FVC < 70% predicted reference value'), 
           ref_symbols = 'd', 
           part = 'body') %>% 
  theme_vanilla
